Preregistration

### 2021-04-14 preregistration.Rmd
add smoothed plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lavaan)
library(furrr)
source(here::here("R", "simulation.R"))
# if you have access to a hpc envir specify this in R/hpc.R
# if not we use local multicore, consider reduce nsim; increase nstep in ↑YAML↑

@@

setup <- expand_grid(n_obs = n_obs,
                     truth = model_truth,
                     same = model_same,
                     differ = model_differ,
                     mod_load = c(3),
                     mod_int = c(3),
                     extract_fns = list(extract_fns),
                     group.equal = list(c("loadings", "intercepts")),
                     auto.fix.first = FALSE)
to_export <- ls_funs() %>% map(get)
to_export <- c(list(setup = setup), to_export)
RNGkind("L'Ecuyer-CMRG")
set.seed(params$seed)
res_raw %<-% 
  generate_data(n_sim,
                setup,
                furrr_options(
                  globals = to_export,
                  seed = params$seed,
                  packages = c("furrr", "lavaan", "tidyverse")
                ))
```

```{r write-out, include=FALSE}
invisible(res_raw)
write_rds(res_raw, here::here("res_raw.rds"))
```

```{r checksum}
# compute checksum using md5
checksum <- digest::digest(res_raw, "md5")
if(checksum != "e3b116b36c2a267d0e848e692b76fc1a"){
  warning("Mismatch between original and current simulations!
          Checksum now is:\n    ", checksum)
}
```

```{r}
res <- res_raw  %>%
  map(bind_rows) %>% 
  bind_rows() %>% 
  unnest(results)

@@

res_interval <- res %>%
  select(n_obs, std_estimate, mod_load, mod_int) %>% 
  filter(!is.na(std_estimate)) %>% 
  group_by(n_obs, mod_load, mod_int) %>% 
  summarise(interval = list(interval(std_estimate, seq(0.05, .2, 0.01))), 
            .groups = "drop") %>% 
  unnest(c(interval)) %>% 
  mutate(width = upper - lower)
```

@@

plot_interval
```

```{r}
plot_width <- res_interval %>% 
  ggplot(aes(n_obs, width, color = alpha, group = alpha)) +
  geom_line() +
  scale_color_viridis_c() +
  theme_minimal() +
  scale_y_log10(breaks = seq(0, 0.8, .1)) +
  theme(axis.text.x = element_text(angle = -90)) +
  NULL

plot_width
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)

library(tidyverse)
library(lavaan)
library(furrr)
library(slider)
source(here::here("R", "simulation.R"))
# if you have access to a hpc envir specify this in R/hpc.R
# if not we use local multicore
# to speed up consider reduce nsim; increase nstep in ↑YAML↑

@@

setup <- expand_grid(n_obs = n_obs,
                     truth = model_truth,
                     same = model_same,
                     differ = model_differ,
                     mod_load = c(3),
                     mod_int = c(3),
                     extract_fns = list(extract_fns),
                     group.equal = list(c("loadings", "intercepts")),
                     auto.fix.first = FALSE)
to_export <- ls_funs() %>% map(get)
to_export <- c(list(setup = setup), to_export)
RNGkind("L'Ecuyer-CMRG")
set.seed(params$seed)
res_raw %<-% generate_data_setup(n_sim,
                setup,
                furrr_options(
                  globals = to_export,
                  seed = params$seed,
                  packages = c("furrr", "lavaan", "tidyverse")
                ))
```

```{r write-out, error=TRUE, include=FALSE}
write_rds(res_raw, here::here("res_raw.rds"))
```

```{r checksum}
# compute checksum using md5
checksum <- digest::digest(res_raw, "md5")
if(checksum != "4203854848ad0cc5d2f848c44b70815d"){
  warning("Mismatch between original and current simulations!
Checksum now is:\n    '", checksum, "'")
}
```

```{r}
res <- res_raw  %>%
  map(bind_rows) %>% 
  bind_rows() %>% 
  mutate(results = map(results, "result")) %>% 
  unnest(results)

@@

res_interval <- res %>%
  select(n_obs, std_estimate, mod_load, mod_int) %>% 
  filter(!is.na(std_estimate)) %>% 
  group_by(n_obs, mod_load, mod_int) %>% 
  summarise(interval = list(interval(std_estimate, seq(0.05, .2, 0.01))), 
            .groups = "drop") %>% 
  unnest(c(interval)) %>% 
  mutate(width = upper - lower) %>% 
  group_by(alpha) %>% 
  arrange(n_obs) %>% 
  mutate(across(c(width, upper, lower), list(smooth = ~slide_dbl(.x, mean, na.rm = TRUE, .before = 2, .after = 0, .complete = FALSE)))) %>% 
  ungroup()
```

@@

plot_interval

plot_interval %+% aes(ymin = lower_smooth, ymax = upper_smooth)
```

```{r}
plot_width <- res_interval %>% 
  ggplot(aes(n_obs, width, color = alpha, group = alpha)) +
  geom_line() +
  scale_color_viridis_c() +
  theme_minimal() +
  scale_y_log10(breaks = seq(0, 0.8, .1)) +
  theme(axis.text.x = element_text(angle = -90)) +
  NULL
plot_width
plot_width %+% aes(y = width_smooth)
```
```{r}
res_interval %>% 
  ggplot(aes(n_obs, width, color = alpha, group = alpha)) +
  geom_smooth(se = FALSE, span = .1, size = .5) +
  scale_color_viridis_c() +
  theme_minimal() +
  scale_y_log10(breaks = seq(0, 0.8, .1)) +
  theme(axis.text.x = element_text(angle = -90)) +
  NULL
```
